KIN: A method to infer relatedness from low-coverage ancient DNA

### 2022-09-11 paper_overleaf/KIN_a_method_to_estimate_relatedness_from_low_coverage_data_supplements.tex
Updates from Overleaf

\begin{figure}[h!]
    \includegraphics[width=18cm]{supplementary_info/plots/contam0_inbred1_run57_coverage0.2_asc0_inputMode_hapProbs_fil0_pair0_15_relid_betaplot.png}
    \centering
    \caption{Comparison of beta distributions estimated with the Identical KIN-HMM (left) without and (right) with variance constrained optimization of $\delta$ parameters.The histogram in each plot shows pairwise differences in genomic windows for identical individuals. Colored lines shows the Beta probability distribution for each $i$, where $i$ is the index used for combinations of $Z_w$ and $H_w$.}
    \label{figS4:bndsbeta}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/contam_missspecification.png}
    \caption{False positive and true positive rates as a function of incorrect contamination estimates provided to KINgaroo. Dashed vertical line represents true contamination (2.5\%) in simulations, and dotted horizontal line in top panel represents $5\%$ false positive rate.}
    \label{figS10:cnt}
\end{figure}

>>>>

\begin{figure}[h!]
    \includegraphics[width=18cm]{supplementary_info/plots/contam0_inbred1_run57_coverage0.2_asc0_inputMode_hapProbs_fil0_pair0_15_relid_betaplot1.png}
    \centering
    \caption{Comparison of beta distributions estimated with the Identical KIN-HMM (left) without and (right) with variance constrained optimization of $\delta$ parameters.The histogram in each plot shows pairwise differences in genomic windows for identical individuals. Colored lines shows the Beta probability distribution for each $i$, where $i$ is the index used for combinations of $Z_w$ and $H_w$.}
    \label{figS4:bndsbeta}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/contam_missspecification.png}
    \caption{False positive and true positive rates as a function of incorrect contamination estimates provided to the ROH-HMM. Dashed vertical line represents true contamination (2.5\%) in simulations, and dotted horizontal line in top panel represents $5\%$ false positive rate.}
    \label{figS10:cnt}
\end{figure}
